### 2017-04-02 Docs/Papers/Technical/arxiv/v1/main.tex
sub_v2

%%%%%%%%%%%%%%%%%%%%
\subsection{Keywords relevance estimation}
\label{keywords_est}
\paragraph{Relevance definition}

@@

\paragraph{Moving window estimation}
The previous scores are estimated on a moving window with fixed time length following the idea that the present relevance is given by the most recent context and thus that the influence vanishes when going further into the past. Consequently, the co-occurrence matrix is chosen to be constructed at year $t$ restricting to patent which applied during the time window $\big[ t - T_0 ; t \big]$. Note that the causal property of the window is crucial as the future cannot play any role in the current state of keywords and patents. This way, we will obtain semantic classes which are exploitable on a $T_0$ time span. For example, this enables us to compute the modularity of classes in the citation network as in section \ref{citationmodularity}. In the following, we take $T_0 = 4$ (which corresponds to a five year window) consistently with the choice of maximum time lag for citations made in Section \ref{sub:citation}. Accordingly, the sensitivity analysis for $T_0=2$ can be found in Appendix~\nameref{app:sensitivity}.

@@

\paragraph{Intra-classification overlaps}

@@

\paragraph{Inter-classification overlaps}

@@

\textbf{Vector file of the semantic network (Fig.\ref{fig:rawnetwork})} available at \texttt{http://37.187.242.99/files/public/network.svg}

@@

\paragraph{Sample restriction}
As explained briefly before, we consider every patent granted by the USPTO between 1976 and 2013. For each patent, we gather information on the year of application, the year the patent was granted, the name of the inventors, the name of the assignees and the technological fields in which the patent has been classified (we get back to what these fields are below). We restrict attention to patents applied for before 2007. The choice of the year 2007 is due to the truncation bias: we only want to use information on granted patents and we get rid of all patents that were rejected by the USPTO. However, in order to date them as closely as possible to the date of invention, we use the application date as a reference. As a consequence, as we approach the end of the sample, we only observe a fraction of the patents which have been granted by 2013. Looking at the distribution of time lag between application and grant in the past and assuming that this distribution is complete in time, we can consider that data prior to 2007 are almost complete and that data for 2007 are complete up to 90\%.

@@

\paragraph{Setup}

@@

\paragraph{Running}

@@

\paragraph{Options}

@@

\paragraph{Tasks}

@@

\paragraph{Classification Data}

The data resulting from the classification process with parameters used here is available as \texttt{csv} files at \url{http://37.187.242.99/files/public/classification_window5_kwLimit100000_dispth0.06_ethunit4.1e-05.zip}. Each files are named according to their content (keywords, patent probabilities, patent measures) and the corresponding time window. The format are the following :

@@

\paragraph{Analysis}

>>>>

%%%%%%%%%%%%%%%%%%%%
\subsection{Keywords relevance estimation}
\label{keywords_est}
\paragraph*{Relevance definition}

@@

\paragraph*{Moving window estimation}
The previous scores are estimated on a moving window with fixed time length following the idea that the present relevance is given by the most recent context and thus that the influence vanishes when going further into the past. Consequently, the co-occurrence matrix is chosen to be constructed at year $t$ restricting to patent which applied during the time window $\big[ t - T_0 ; t \big]$. Note that the causal property of the window is crucial as the future cannot play any role in the current state of keywords and patents. This way, we will obtain semantic classes which are exploitable on a $T_0$ time span. For example, this enables us to compute the modularity of classes in the citation network as in section \ref{citationmodularity}. In the following, we take $T_0 = 4$ (which corresponds to a five year window) consistently with the choice of maximum time lag for citations made in Section \ref{sub:citation}. Accordingly, the sensitivity analysis for $T_0=2$ can be found in Appendix~\nameref{app:sensitivity}.

@@

\paragraph*{Intra-classification overlaps}

@@

\paragraph*{Inter-classification overlaps}

@@

\textbf{Vector file of the semantic network (Fig.\ref{fig:rawnetwork})} available at\\
 \url{http://37.187.242.99/files/public/network.svg}

@@

\paragraph*{Sample restriction}
As explained briefly before, we consider every patent granted by the USPTO between 1976 and 2013. For each patent, we gather information on the year of application, the year the patent was granted, the name of the inventors, the name of the assignees and the technological fields in which the patent has been classified (we get back to what these fields are below). We restrict attention to patents applied for before 2007. The choice of the year 2007 is due to the truncation bias: we only want to use information on granted patents and we get rid of all patents that were rejected by the USPTO. However, in order to date them as closely as possible to the date of invention, we use the application date as a reference. As a consequence, as we approach the end of the sample, we only observe a fraction of the patents which have been granted by 2013. Looking at the distribution of time lag between application and grant in the past and assuming that this distribution is complete in time, we can consider that data prior to 2007 are almost complete and that data for 2007 are complete up to 90\%.

@@

\paragraph*{Setup}

@@

\paragraph*{Running}

@@

\paragraph*{Options}

@@

\paragraph*{Tasks}

@@

\paragraph*{Classification Data}

The data resulting from the classification process with parameters used here is available as \texttt{csv} files at\\
 \url{http://37.187.242.99/files/public/classification_window5_kwLimit100000_dispth0.06_ethunit4.1e-05.zip}. Each files are named according to their content (keywords, patent probabilities, patent measures) and the corresponding time window. The format are the following :

@@

\paragraph*{Analysis}
